State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2020-09-17 analysis/paper/paper.Rmd
cleaned up some extraneous lines

<!-- The following line inserts a page break  -->
\newpage

@@

p1 = ggplot(data.frame(x = c(-5, 8)),
            aes(x)) +
  stat_function(fun = dnorm,
                args = list(mean = 4, sd = 0.4),
                aes(color = 'Daytime Fish'),
                lwd = 2) +
  stat_function(fun = dnorm,
                args = list(mean = 6, sd = 0.55),
                aes(color = 'Total Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = 5, sd = 0.6),
                aes(color = 'Unique Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique Wild Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique Hatchery Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique HNC Fish'),
                geom = 'blank') +
  # scale_color_brewer(palette = 'Set1') +
  # scale_color_viridis_d() +
  scale_color_brewer(palette = "Spectral") +
  # scale_color_grey(start = 0.9,
  #                  end = 0.3) +
  geom_vline(xintercept = 4,
             linetype = 2) +
  coord_cartesian(xlim = my_xlim,
                  ylim = my_ylim) +
  # theme_classic() +
  theme_pubr(legend = "bottom") +
  guides(color = guide_legend(nrow = 3,
                              title.position = 'top')) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank()) +
  labs(x = 'Escapement',
       color = 'Fish Type',
       title = '   Daytime Fish')

@@

examp_p
```

>>>>

@@

# choose appropriate color scale for color vs. black & white
p1 = ggplot(data.frame(x = c(-5, 8)),
            aes(x)) +
  stat_function(fun = dnorm,
                args = list(mean = 4, sd = 0.4),
                aes(color = 'Daytime Fish'),
                lwd = 2) +
  stat_function(fun = dnorm,
                args = list(mean = 6, sd = 0.55),
                aes(color = 'Total Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = 5, sd = 0.6),
                aes(color = 'Unique Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique Wild Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique Hatchery Fish'),
                geom = 'blank') +
  stat_function(fun = dnorm,
                args = list(mean = -1, sd = 0.75),
                aes(color = 'Unique HNC Fish'),
                geom = 'blank') +
  scale_color_brewer(palette = "Spectral") +
  # scale_color_grey(start = 0.9,
  #                  end = 0.3) +
  geom_vline(xintercept = 4,
             linetype = 2) +
  coord_cartesian(xlim = my_xlim,
                  ylim = my_ylim) +
  theme_pubr(legend = "bottom") +
  guides(color = guide_legend(nrow = 3,
                              title.position = 'top')) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank()) +
  labs(x = 'Escapement',
       color = 'Fish Type',
       title = '   Daytime Fish')

@@

examp_p
